FISTA with adaptive discretisations

### 2021-01-21 paper.tex
quick sync

\section{Introduction}
The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was proposed by \citet{Beck2009}
as an extension of Nesterov's fast gradient method (see~\cite{Nesterov2004})
and is now a very popular algorithm for minimising the sum of two convex functions.
We write this as the problem of computing 
\begin{equation}\label{eq: min F = fD+fC}
	u^* \in \argmin_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
\end{equation}
where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function, whose ``proximity operator'' is easy to compute.
The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$.
% when $u^*\in \F H$ is finite dimensional and
\cite{Chambolle2015} showed (up to a minor modification) convergence of the iterates in
a general Hibert space setting.
% extended this result to the general Hilbert space setting.
Many further works have gone on to demonstrate %even
faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\section{Introduction}
The Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) was first proposed by \citet{Beck2009} and is now a very popular algorithm for minimising the sum of two convex functions. We will write this as the problem of computing 
\begin{equation}\label{eq: min F = fD+fC}
	u^* \in \argmin_{\varf0\in\F H}\Func0(\varf0)  \qquad\text{such that}\qquad \Func0(\varf0)\coloneqq \func1(\varf0) + \func2(\varf0),
\end{equation}
where $\func1\colon\F H\to\R$ is a convex differentiable function with $L$-Lipschitz gradient and $\func2\colon\F H\to\bar\R$ is a convex function. The iterates of the FISTA algorithm will be denoted $\varf0_n\in\F H$. \citet{Beck2009} showed that $\Func0(\varf0_n) - \Func0(\varf0^*)$ converges at the optimum rate of $n^{-2}$ when $u^*\in \F H$ is finite dimensional and \cite{Chambolle2015} extended this result to the general Hilbert space setting. Many further works have gone on to demonstrate even faster practical convergence rates for slightly modified variants of FISTA \citep{Tao2016,Liang2017,Alamo2019}.

@@

\end{document}
